Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-06-04 paper2.qmd
section:6; process:write

## Further research {#sec-discussion_RA}

Four current and new research avenues deserve particular attention due to their direct impact on the reliability and validity of trait estimates and the accuracy of statistical inferences. The following sections outline these avenues and explain how our model provides a rigorous research framework to investigate them.

>>>>

## Future research {#sec-discussion_RA}

Among the many potential directions for future research, four avenues, both current and new, deserve particular attention due to their direct impact on the reliability and validity of trait estimates, as well as on the accuracy of statistical inferences. The following sections outline these avenues and explain how our model provides a rigorous research framework to investigate them.
